---
title: "DE_pipeline_LU"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = TRUE)
```

```{r eval=T, echo=F, message=FALSE, warning=FALSE}
require(sleuth)
require(ggvenn)
require(tidyverse)
require(XGR)
require(readxl)
```

```{r, warning=FALSE}
dir.create('DE/OUT_LU')
```


## Load the data

```{r, eval=F, echo=TRUE}
sample_id_LU = dir(file.path("DE/kallisto_LU"))

dirs_LU <- sapply(sample_id_LU, function(id) file.path('DE/kallisto_LU', id)) #
cond_LU = rep(c( 'AtF3', 'AtF5', 'AtK3', 'AtK5', 'LMF3', 'LMF5', 'LMK3', 'LMK5'), each = 3)

df_LU = data.frame(sample = sample_id_LU, path = dirs_LU, conditions = cond_LU)
df_LU = df_LU %>% mutate(conditions = as.factor(conditions)) %>% filter(sample != 'LMF3_1.k31')
```

### Function to calculate DE and return table of statistics for each gene

```{r, eval=F, echo=T}
difexpr = function(df, cond_1, cond_2){
  
  df = df[df$conditions %in% c(cond_1, cond_2),]
  
  so = sleuth_prep(df, extra_bootstrap_summary = T, read_bootstrap_tpm = TRUE, ~conditions)
  so = sleuth_fit(so, ~conditions, 'full')
  so = sleuth_fit(so, ~1, 'reduced')
  so = sleuth_lrt(so, 'reduced', 'full')
  
  lfc<- kallisto_table(so) %>%
    group_by(target_id, conditions) %>%
    summarize(mean_ct=mean(est_counts)) %>%
    group_by(target_id) %>% 
    summarise(lFC = log2((mean_ct[conditions==cond_1]+0.01)/(mean_ct[conditions==cond_2]+0.01)))
  
  sleuth_table <- sleuth_results(so, test = "reduced:full", test_type = 'lrt')
  sleuth_table = merge(sleuth_table, lfc, by = 'target_id')
  
  return(sleuth_table)
}
```

## Tables of DE

```{r warning=F, message=F}
tab_LMK5_vs_LMK3 = difexpr(df_LU, 'LMK5', "LMK3")
tab_AtK5_vs_AtK3 = difexpr(df_LU, 'AtK5', "AtK3")
tab_AtK3_vs_LMK3 = difexpr(df_LU, 'AtK3', "LMK3")
tab_AtK5_vs_LMK5 = difexpr(df_LU, 'AtK5', "LMK5")

tab_LMF3_vs_LMK3 = difexpr(df_LU, 'LMF3', "LMK3")
tab_LMF5_vs_LMK5 = difexpr(df_LU, 'LMF5', "LMK5")
tab_AtF3_vs_AtK3 = difexpr(df_LU, 'AtF3', "AtK3")
tab_AtF5_vs_AtK5 = difexpr(df_LU, 'AtF5', "AtK5")

tab_LMF5_vs_LMF3 = difexpr(df_LU, 'LMF5', "LMF3")
tab_AtF5_vs_AtF3 = difexpr(df_LU, 'AtF5', "AtF3")
tab_AtF3_vs_LMF3 = difexpr(df_LU, 'AtF3', "LMF3")
tab_AtF5_vs_LMF5 = difexpr(df_LU, 'AtF5', "LMF5")

```

### Function to filter Significant DE genes

```{r}
sig = function(tab,q, lfc){
  t = tab %>% dplyr::filter(qval <= q, abs(lFC) >= lfc) %>% arrange(qval)
  return(t)}
```

## Filtering

```{r echo=T}
sig_LMK5_vs_LMK3 = sig(tab_LMK5_vs_LMK3, 0.05, 1)
sig_AtK5_vs_AtK3 = sig(tab_AtK5_vs_AtK3, 0.01, 1.25)
sig_AtK3_vs_LMK3 = sig(tab_AtK3_vs_LMK3, 0.05, 1.25)
sig_AtK5_vs_LMK5 = sig(tab_AtK5_vs_LMK5, 0.05, 1.25)

sig_LMF3_vs_LMK3 = sig(tab_LMF3_vs_LMK3, 0.05, 1)
sig_LMF5_vs_LMK5 = sig(tab_LMF5_vs_LMK5, 0.05, 1)
sig_AtF3_vs_AtK3 = sig(tab_AtF3_vs_AtK3, 0.01, 1.25)
sig_AtF5_vs_AtK5 = sig(tab_AtF5_vs_AtK5, 0.01, 1.25)

sig_LMF5_vs_LMF3 = sig(tab_LMF5_vs_LMF3, 0.05, 1)
sig_AtF5_vs_AtF3 = sig(tab_AtF5_vs_AtF3, 0.01, 1.25)
sig_AtF3_vs_LMF3 = sig(tab_AtF3_vs_LMF3, 0.05, 1.25)
sig_AtF5_vs_LMF5 = sig(tab_AtF5_vs_LMF5, 0.05, 1.25)
```

### Up- and Downregulated genes filtering

```{r}
sig_LMK5_vs_LMK3_up = sig_LMK5_vs_LMK3 %>% filter(lFC >= 1)
sig_AtK5_vs_AtK3_up = sig_AtK5_vs_AtK3 %>% filter(lFC >= 1.25)
sig_AtK3_vs_LMK3_up = sig_AtK3_vs_LMK3 %>% filter(lFC >= 1.25)
sig_AtK5_vs_LMK5_up = sig_AtK5_vs_LMK5 %>% filter(lFC >= 1.25)

sig_LMF3_vs_LMK3_up = sig_LMF3_vs_LMK3 %>% filter(lFC >= 1)
sig_LMF5_vs_LMK5_up = sig_LMF5_vs_LMK5 %>% filter(lFC >= 1)
sig_AtF3_vs_AtK3_up = sig_AtF3_vs_AtK3 %>% filter(lFC >= 1.25)
sig_AtF5_vs_AtK5_up = sig_AtF5_vs_AtK5 %>% filter(lFC >= 1.25)

sig_LMF5_vs_LMF3_up = sig_LMF5_vs_LMF3 %>% filter(lFC >= 1)
sig_AtF5_vs_AtF3_up = sig_AtF5_vs_AtF3 %>% filter(lFC >= 1.25)
sig_AtF3_vs_LMF3_up = sig_AtF3_vs_LMF3 %>% filter(lFC >= 1.25)
sig_AtF5_vs_LMF5_up = sig_AtF5_vs_LMF5 %>% filter(lFC >= 1.25)
```

```{r}
sig_LMK5_vs_LMK3_down = sig_LMK5_vs_LMK3 %>% filter(lFC <= -1)
sig_AtK5_vs_AtK3_down = sig_AtK5_vs_AtK3 %>% filter(lFC <= -1.25)
sig_AtK3_vs_LMK3_down = sig_AtK3_vs_LMK3 %>% filter(lFC <= -1.25)
sig_AtK5_vs_LMK5_down = sig_AtK5_vs_LMK5 %>% filter(lFC <= -1.25)

sig_LMF3_vs_LMK3_down = sig_LMF3_vs_LMK3 %>% filter(lFC <= -1)
sig_LMF5_vs_LMK5_down = sig_LMF5_vs_LMK5 %>% filter(lFC <= -1)
sig_AtF3_vs_AtK3_down = sig_AtF3_vs_AtK3 %>% filter(lFC <= -1.25)
sig_AtF5_vs_AtK5_down = sig_AtF5_vs_AtK5 %>% filter(lFC <= -1.25)

sig_LMF5_vs_LMF3_down = sig_LMF5_vs_LMF3 %>% filter(lFC <= -1)
sig_AtF5_vs_AtF3_down = sig_AtF5_vs_AtF3 %>% filter(lFC <= -1.25)
sig_AtF3_vs_LMF3_down = sig_AtF3_vs_LMF3 %>% filter(lFC <= -1.25)
sig_AtF5_vs_LMF5_down = sig_AtF5_vs_LMF5 %>% filter(lFC <= -1.25)
```

### Loading the annotation table. Gene Ontology

```{r}
new_xl = readxl::read_xlsx('Annotation_tables/Lu_2_go.xlsx', col_names = c ('gene', 'name', 'description')) %>% select(gene, description)
# new_xl = xl[-1,]
```

### Annotation function

```{r}
annot_lu = function(sig, title, annotation_table){
  
  signames = as.data.frame(sig[1])
  
  xsig = xEnricherYours(signames, annotation_table, 
                        size.range=c(10,2000),
                        min.overlap = 3,
                        test = "hypergeo",
                        p.adjust.method = 'BH', silent = T)

  table_sig <-  xEnrichViewer(xsig, sortBy = 'adjp', 
                               top_num = nrow(xsig$term_info))
  
  if(!is.null(table_sig)){
    table_sig <- table_sig %>% filter(adjp<0.01) %>% rename(description = name)
    
    rownames(table_sig) = NULL
    plot(xEnrichBarplot(xsig, displayBy = 'fdr', 
                        FDR.cutoff = 0.01, font.family = 'Times',
                        bar.label.size = 5, 
                        top_num = 10, bar.width = .8) + ggtitle(title)) 
  }
  return(as.data.frame(table_sig))
}
```

## Annotating GO

```{r, warning=FALSE}
dir.create('DE/OUT_LU/OUT_Annot')
```

```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_ALL.pdf', width = 12, family = "Times")
annot_LMK5_vs_LMK3 = annot_lu(sig_LMK5_vs_LMK3, 'LMK5_vs_LMK3 ALL', new_xl)
annot_AtK5_vs_AtK3 = annot_lu(sig_AtK5_vs_AtK3, 'AtK5_vs_AtK3 ALL', new_xl)
annot_AtK3_vs_LMK3 = annot_lu(sig_AtK3_vs_LMK3, 'AtK3_vs_LMK3 ALL', new_xl) 
annot_AtK5_vs_LMK5 = annot_lu(sig_AtK5_vs_LMK5, 'AtK5_vs_LMK5 ALL', new_xl)

annot_LMF3_vs_LMK3 = annot_lu(sig_LMF3_vs_LMK3, 'LMF3_vs_LMK3 ALL', new_xl)
annot_LMF5_vs_LMK5 = annot_lu(sig_LMF5_vs_LMK5, 'LMF5_vs_LMK5 ALL', new_xl)
annot_AtF3_vs_AtK3 = annot_lu(sig_AtF3_vs_AtK3, 'AtF3_vs_AtK3 ALL', new_xl) 
annot_AtF5_vs_AtK5 = annot_lu(sig_AtF5_vs_AtK5, 'AtF5_vs_AtK5 ALL', new_xl)

annot_LMF5_vs_LMF3 = annot_lu(sig_LMF5_vs_LMF3, 'LMF5_vs_LMF3 ALL', new_xl)
annot_AtF5_vs_AtF3 = annot_lu(sig_AtF5_vs_AtF3, 'AtF5_vs_AtF3 ALL', new_xl)
annot_AtF3_vs_LMF3 = annot_lu(sig_AtF3_vs_LMF3, 'AtF3_vs_LMF3 ALL', new_xl) 
annot_AtF5_vs_LMF5 = annot_lu(sig_AtF5_vs_LMF5, 'AtF5_vs_LMF5 ALL', new_xl)
dev.off()
```


```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_Upregulated.pdf', width = 12, family = "Times")
annot_LMK5_vs_LMK3_up = annot_lu(sig_LMK5_vs_LMK3_up, 'LMK5_vs_LMK3 Upregulated', new_xl)
annot_AtK5_vs_AtK3_up = annot_lu(sig_AtK5_vs_AtK3_up, 'AtK5_vs_AtK3 Upregulated', new_xl)
annot_AtK3_vs_LMK3_up = annot_lu(sig_AtK3_vs_LMK3_up, 'AtK3_vs_LMK3 Upregulated', new_xl) 
annot_AtK5_vs_LMK5_up = annot_lu(sig_AtK5_vs_LMK5_up, 'AtK5_vs_LMK5 Upregulated', new_xl)

annot_LMF3_vs_LMK3_up = annot_lu(sig_LMF3_vs_LMK3_up, 'LMF3_vs_LMK3 Upregulated', new_xl)
annot_LMF5_vs_LMK5_up = annot_lu(sig_LMF5_vs_LMK5_up, 'LMF5_vs_LMK5 Upregulated', new_xl)
annot_AtF3_vs_AtK3_up = annot_lu(sig_AtF3_vs_AtK3_up, 'AtF3_vs_AtK3 Upregulated', new_xl) 
annot_AtF5_vs_AtK5_up = annot_lu(sig_AtF5_vs_AtK5_up, 'AtF5_vs_AtK5 Upregulated', new_xl)

annot_LMF5_vs_LMF3_up = annot_lu(sig_LMF5_vs_LMF3_up, 'LMF5_vs_LMF3 Upregulated', new_xl)
annot_AtF5_vs_AtF3_up = annot_lu(sig_AtF5_vs_AtF3_up, 'AtF5_vs_AtF3 Upregulated', new_xl)
annot_AtF3_vs_LMF3_up = annot_lu(sig_AtF3_vs_LMF3_up, 'AtF3_vs_LMF3 Upregulated', new_xl) 
annot_AtF5_vs_LMF5_up = annot_lu(sig_AtF5_vs_LMF5_up, 'AtF5_vs_LMF5 Upregulated', new_xl)
dev.off()
```


```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_Downregulated.pdf', width = 12, family = "Times")
annot_LMK5_vs_LMK3_down = annot_lu(sig_LMK5_vs_LMK3_down, 'LMK5_vs_LMK3 Downregulated', new_xl)
annot_AtK5_vs_AtK3_down = annot_lu(sig_AtK5_vs_AtK3_down, 'AtK5_vs_AtK3 Downregulated', new_xl)
annot_AtK3_vs_LMK3_down = annot_lu(sig_AtK3_vs_LMK3_down, 'AtK3_vs_LMK3 Downregulated', new_xl) 
annot_AtK5_vs_LMK5_down = annot_lu(sig_AtK5_vs_LMK5_down, 'AtK5_vs_LMK5 Downregulated', new_xl)

annot_LMF3_vs_LMK3_down = annot_lu(sig_LMF3_vs_LMK3_down, 'LMF3_vs_LMK3 Downregulated', new_xl)
annot_LMF5_vs_LMK5_down = annot_lu(sig_LMF5_vs_LMK5_down, 'LMF5_vs_LMK5 Downregulated', new_xl)
annot_AtF3_vs_AtK3_down = annot_lu(sig_AtF3_vs_AtK3_down, 'AtF3_vs_AtK3 Downregulated', new_xl) 
annot_AtF5_vs_AtK5_down = annot_lu(sig_AtF5_vs_AtK5_down, 'AtF5_vs_AtK5 Downregulated', new_xl)

annot_LMF5_vs_LMF3_down = annot_lu(sig_LMF5_vs_LMF3_down, 'LMF5_vs_LMF3 Downregulated', new_xl)
annot_AtF5_vs_AtF3_down = annot_lu(sig_AtF5_vs_AtF3_down, 'AtF5_vs_AtF3 Downregulated', new_xl)
annot_AtF3_vs_LMF3_down = annot_lu(sig_AtF3_vs_LMF3_down, 'AtF3_vs_LMF3 Downregulated', new_xl) 
annot_AtF5_vs_LMF5_down = annot_lu(sig_AtF5_vs_LMF5_down, 'AtF5_vs_LMF5 Downregulated', new_xl)
dev.off()
```


### Loading the annotation table. Plant Reactome

```{r}
reactome = read_xlsx('./Annotation_tables/reactome_joint.xlsx')
```

## Annotating Reactome

```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_Reactome_ALL.pdf', width = 12, family = "Times")
reactome_LMK5_vs_LMK3 = annot_lu(sig_LMK5_vs_LMK3, 'LMK5_vs_LMK3 ALL', reactome)
reactome_AtK5_vs_AtK3 = annot_lu(sig_AtK5_vs_AtK3, 'AtK5_vs_AtK3 ALL', reactome)
reactome_AtK3_vs_LMK3 = annot_lu(sig_AtK3_vs_LMK3, 'AtK3_vs_LMK3 ALL', reactome) 
reactome_AtK5_vs_LMK5 = annot_lu(sig_AtK5_vs_LMK5, 'AtK5_vs_LMK5 ALL', reactome)

reactome_LMF3_vs_LMK3 = annot_lu(sig_LMF3_vs_LMK3, 'LMF3_vs_LMK3 ALL', reactome)
reactome_LMF5_vs_LMK5 = annot_lu(sig_LMF5_vs_LMK5, 'LMF5_vs_LMK5 ALL', reactome)
reactome_AtF3_vs_AtK3 = annot_lu(sig_AtF3_vs_AtK3, 'AtF3_vs_AtK3 ALL', reactome) 
reactome_AtF5_vs_AtK5 = annot_lu(sig_AtF5_vs_AtK5, 'AtF5_vs_AtK5 ALL', reactome)

reactome_LMF5_vs_LMF3 = annot_lu(sig_LMF5_vs_LMF3, 'LMF5_vs_LMF3 ALL', reactome)
reactome_AtF5_vs_AtF3 = annot_lu(sig_AtF5_vs_AtF3, 'AtF5_vs_AtF3 ALL', reactome)
reactome_AtF3_vs_LMF3 = annot_lu(sig_AtF3_vs_LMF3, 'AtF3_vs_LMF3 ALL', reactome) 
reactome_AtF5_vs_LMF5 = annot_lu(sig_AtF5_vs_LMF5, 'AtF5_vs_LMF5 ALL', reactome)
dev.off()
```


```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_Reactome_Upregulated.pdf', width = 12, family = "Times")
reactome_LMK5_vs_LMK3_up = annot_lu(sig_LMK5_vs_LMK3_up, 'LMK5_vs_LMK3 Upregulated', reactome)
reactome_AtK5_vs_AtK3_up = annot_lu(sig_AtK5_vs_AtK3_up, 'AtK5_vs_AtK3 Upregulated', reactome)
reactome_AtK3_vs_LMK3_up = annot_lu(sig_AtK3_vs_LMK3_up, 'AtK3_vs_LMK3 Upregulated', reactome) 
reactome_AtK5_vs_LMK5_up = annot_lu(sig_AtK5_vs_LMK5_up, 'AtK5_vs_LMK5 Upregulated', reactome)

reactome_LMF3_vs_LMK3_up = annot_lu(sig_LMF3_vs_LMK3_up, 'LMF3_vs_LMK3 Upregulated', reactome)
reactome_LMF5_vs_LMK5_up = annot_lu(sig_LMF5_vs_LMK5_up, 'LMF5_vs_LMK5 Upregulated', reactome)
reactome_AtF3_vs_AtK3_up = annot_lu(sig_AtF3_vs_AtK3_up, 'AtF3_vs_AtK3 Upregulated', reactome) 
reactome_AtF5_vs_AtK5_up = annot_lu(sig_AtF5_vs_AtK5_up, 'AtF5_vs_AtK5 Upregulated', reactome)

reactome_LMF5_vs_LMF3_up = annot_lu(sig_LMF5_vs_LMF3_up, 'LMF5_vs_LMF3 Upregulated', reactome)
reactome_AtF5_vs_AtF3_up = annot_lu(sig_AtF5_vs_AtF3_up, 'AtF5_vs_AtF3 Upregulated', reactome)
reactome_AtF3_vs_LMF3_up = annot_lu(sig_AtF3_vs_LMF3_up, 'AtF3_vs_LMF3 Upregulated', reactome) 
reactome_AtF5_vs_LMF5_up = annot_lu(sig_AtF5_vs_LMF5_up, 'AtF5_vs_LMF5 Upregulated', reactome)
dev.off()
```


```{r fig.height=6, fig.width=12, warning=F, message=FALSE}
pdf('DE/OUT_LU/OUT_Annot/Barplots_Reactome_Downregulated.pdf', width = 12, family = "Times")
reactome_LMK5_vs_LMK3_down = annot_lu(sig_LMK5_vs_LMK3_down, 'LMK5_vs_LMK3 Downregulated', reactome)
reactome_AtK5_vs_AtK3_down = annot_lu(sig_AtK5_vs_AtK3_down, 'AtK5_vs_AtK3 Downregulated', reactome)
reactome_AtK3_vs_LMK3_down = annot_lu(sig_AtK3_vs_LMK3_down, 'AtK3_vs_LMK3 Downregulated', reactome) 
reactome_AtK5_vs_LMK5_down = annot_lu(sig_AtK5_vs_LMK5_down, 'AtK5_vs_LMK5 Downregulated', reactome)

reactome_LMF3_vs_LMK3_down = annot_lu(sig_LMF3_vs_LMK3_down, 'LMF3_vs_LMK3 Downregulated', reactome)
reactome_LMF5_vs_LMK5_down = annot_lu(sig_LMF5_vs_LMK5_down, 'LMF5_vs_LMK5 Downregulated', reactome)
reactome_AtF3_vs_AtK3_down = annot_lu(sig_AtF3_vs_AtK3_down, 'AtF3_vs_AtK3 Downregulated', reactome) 
reactome_AtF5_vs_AtK5_down = annot_lu(sig_AtF5_vs_AtK5_down, 'AtF5_vs_AtK5 Downregulated', reactome)

reactome_LMF5_vs_LMF3_down = annot_lu(sig_LMF5_vs_LMF3_down, 'LMF5_vs_LMF3 Downregulated', reactome)
reactome_AtF5_vs_AtF3_down = annot_lu(sig_AtF5_vs_AtF3_down, 'AtF5_vs_AtF3 Downregulated', reactome)
reactome_AtF3_vs_LMF3_down = annot_lu(sig_AtF3_vs_LMF3_down, 'AtF3_vs_LMF3 Downregulated', reactome) 
reactome_AtF5_vs_LMF5_down = annot_lu(sig_AtF5_vs_LMF5_down, 'AtF5_vs_LMF5 Downregulated', reactome)
dev.off()
```


## Making some lists

```{r}
titles = c("LMK5_vs_LMK3", "AtK5_vs_AtK3", "AtK3_vs_LMK3", "AtK5_vs_LMK5",
           "LMF3_vs_LMK3", "LMF5_vs_LMK5", "AtF3_vs_AtK3", "AtF5_vs_AtK5",
           "LMF5_vs_LMF3", "AtF5_vs_AtF3", "AtF3_vs_LMF3", "AtF5_vs_LMF5")

v_tabs = list(tab_LMK5_vs_LMK3, tab_AtK5_vs_AtK3, tab_AtK3_vs_LMK3, tab_AtK5_vs_LMK5,
           tab_LMF3_vs_LMK3, tab_LMF5_vs_LMK5, tab_AtF3_vs_AtK3, tab_AtF5_vs_AtK5,
           tab_LMF5_vs_LMF3, tab_AtF5_vs_AtF3, tab_AtF3_vs_LMF3, tab_AtF5_vs_LMF5)

v_sigs = list(sig_LMK5_vs_LMK3, sig_AtK5_vs_AtK3, sig_AtK3_vs_LMK3, sig_AtK5_vs_LMK5,
           sig_LMF3_vs_LMK3, sig_LMF5_vs_LMK5, sig_AtF3_vs_AtK3, sig_AtF5_vs_AtK5,
           sig_LMF5_vs_LMF3, sig_AtF5_vs_AtF3, sig_AtF3_vs_LMF3, sig_AtF5_vs_LMF5)

v_sigs_up = list(sig_LMK5_vs_LMK3_up, sig_AtK5_vs_AtK3_up, sig_AtK3_vs_LMK3_up, sig_AtK5_vs_LMK5_up,
           sig_LMF3_vs_LMK3_up, sig_LMF5_vs_LMK5_up, sig_AtF3_vs_AtK3_up, sig_AtF5_vs_AtK5_up,
           sig_LMF5_vs_LMF3_up, sig_AtF5_vs_AtF3_up, sig_AtF3_vs_LMF3_up, sig_AtF5_vs_LMF5_up)

v_sigs_down = list(sig_LMK5_vs_LMK3_down, sig_AtK5_vs_AtK3_down, sig_AtK3_vs_LMK3_down, sig_AtK5_vs_LMK5_down,
           sig_LMF3_vs_LMK3_down, sig_LMF5_vs_LMK5_down, sig_AtF3_vs_AtK3_down, sig_AtF5_vs_AtK5_down,
           sig_LMF5_vs_LMF3_down, sig_AtF5_vs_AtF3_down, sig_AtF3_vs_LMF3_down, sig_AtF5_vs_LMF5_down)

v_annots = list(annot_LMK5_vs_LMK3, annot_AtK5_vs_AtK3, annot_AtK3_vs_LMK3, annot_AtK5_vs_LMK5,
           annot_LMF3_vs_LMK3, annot_LMF5_vs_LMK5, annot_AtF3_vs_AtK3, annot_AtF5_vs_AtK5,
           annot_LMF5_vs_LMF3, annot_AtF5_vs_AtF3, annot_AtF3_vs_LMF3, annot_AtF5_vs_LMF5)

v_annots_up = list(annot_LMK5_vs_LMK3_up, annot_AtK5_vs_AtK3_up, annot_AtK3_vs_LMK3_up, annot_AtK5_vs_LMK5_up,
           annot_LMF3_vs_LMK3_up, annot_LMF5_vs_LMK5_up, annot_AtF3_vs_AtK3_up, annot_AtF5_vs_AtK5_up,
           annot_LMF5_vs_LMF3_up, annot_AtF5_vs_AtF3_up, annot_AtF3_vs_LMF3_up, annot_AtF5_vs_LMF5_up)

v_annots_down = list(annot_LMK5_vs_LMK3_down, annot_AtK5_vs_AtK3_down, annot_AtK3_vs_LMK3_down, annot_AtK5_vs_LMK5_down,
           annot_LMF3_vs_LMK3_down, annot_LMF5_vs_LMK5_down, annot_AtF3_vs_AtK3_down, annot_AtF5_vs_AtK5_down,
           annot_LMF5_vs_LMF3_down, annot_AtF5_vs_AtF3_down, annot_AtF3_vs_LMF3_down, annot_AtF5_vs_LMF5_down)

v_reactomes = list(reactome_LMK5_vs_LMK3, reactome_AtK5_vs_AtK3, reactome_AtK3_vs_LMK3, reactome_AtK5_vs_LMK5,
                reactome_LMF3_vs_LMK3, reactome_LMF5_vs_LMK5, reactome_AtF3_vs_AtK3, reactome_AtF5_vs_AtK5,
                reactome_LMF5_vs_LMF3, reactome_AtF5_vs_AtF3, reactome_AtF3_vs_LMF3, reactome_AtF5_vs_LMF5)

v_reactomes_up = list(reactome_LMK5_vs_LMK3_up, reactome_AtK5_vs_AtK3_up, reactome_AtK3_vs_LMK3_up, reactome_AtK5_vs_LMK5_up,
                   reactome_LMF3_vs_LMK3_up, reactome_LMF5_vs_LMK5_up, reactome_AtF3_vs_AtK3_up, reactome_AtF5_vs_AtK5_up,
                   reactome_LMF5_vs_LMF3_up, reactome_AtF5_vs_AtF3_up, reactome_AtF3_vs_LMF3_up, reactome_AtF5_vs_LMF5_up)

v_reactomes_down = list(reactome_LMK5_vs_LMK3_down, reactome_AtK5_vs_AtK3_down, reactome_AtK3_vs_LMK3_down, reactome_AtK5_vs_LMK5_down,
                     reactome_LMF3_vs_LMK3_down, reactome_LMF5_vs_LMK5_down, reactome_AtF3_vs_AtK3_down, reactome_AtF5_vs_AtK5_down,
                     reactome_LMF5_vs_LMF3_down, reactome_AtF5_vs_AtF3_down, reactome_AtF3_vs_LMF3_down, reactome_AtF5_vs_LMF5_down)

names(v_tabs) = titles 
names(v_sigs) = titles 
names(v_sigs_up) = titles 
names(v_sigs_down) = titles
names(v_annots) = titles 
names(v_annots_up) = titles 
names(v_annots_down) = titles
names(v_annots) = titles 
names(v_annots_up) = titles 
names(v_annots_down) = titles 

```

### RDS files

```{r}
saveRDS(titles, 'RDS_files/titles.rds')
saveRDS(v_sigs, 'RDS_files/v_sigs.rds')
saveRDS(v_annots, 'RDS_files/v_annots.rds')
saveRDS(v_reactomes, 'RDS_files/v_reactomes.rds')
```

## Writing Tables function

```{r}
write_tables_lu = function(table, step, title, regulation=NULL, reactome=F){
  if (step == 'DE'){
    divider = '_DE_'
  } else if(step == 'Annot'){
    if (reactome){
      divider = '_Reactome_'
    }
    else{
      divider = '_GO_'
    }
    
  } else{
   divider = '_all_genes_'
  }
  
  writexl::write_xlsx(table, path = file.path('DE/OUT_LU/', 
                                              paste('OUT_', step, sep=''),
                                              paste(title, divider, regulation, '.xlsx', sep='')))
}
```

# Tables .xlsx

```{r, warning=FALSE}
dir.create('DE/OUT_LU/OUT_all')
dir.create('DE/OUT_LU/OUT_DE')
```

```{r}
for (i in 1:12){
  write_tables_lu(v_tabs[[i]], step = 'all', title = titles[i])
}
```


```{r}
for (i in 1:12){
  write_tables_lu(v_sigs[[i]], step = 'DE', title = titles[i], regulation = 'ALL')
}

for (i in 1:12){
  write_tables_lu(v_sigs_up[[i]], step = 'DE', title = titles[i], regulation = 'Upregulated')
}

for (i in 1:12){
  write_tables_lu(v_sigs_down[[i]], step = 'DE', title = titles[i], regulation = 'Downregulated')
}
```


```{r}
for (i in 1:12){
  write_tables_lu(v_annots[[i]], step = 'Annot', title = titles[i], regulation = 'ALL')
}

for (i in 1:12){
  write_tables_lu(v_annots_up[[i]], step = 'Annot', title = titles[i], regulation = 'Upregulated')
}

for (i in 1:12){
  write_tables_lu(v_annots_down[[i]], step = 'Annot', title = titles[i], regulation = 'Downregulated')
}

```

```{r}
for (i in 1:12){
  write_tables_lu(v_reactomes[[i]], step = 'Annot', title = titles[i], regulation = 'ALL', reactome=T)
}

for (i in 1:12){
  write_tables_lu(v_reactomes_up[[i]], step = 'Annot', title = titles[i], regulation = 'Upregulated', reactome=T)
}

for (i in 1:12){
  write_tables_lu(v_reactomes_down[[i]], step = 'Annot', title = titles[i], regulation = 'Downregulated', reactome=T)
}
```

