---
title: "Quality Control"
output:
  html_document:
    toc: yes
    fig_width: 6
    df_print: kable
    fig_height: 6
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: inline
---

**package insatallation**

```{r, echo=T, message=FALSE} 
library(methylKit)
library(ggplot2)
```


## Script that evaluated on CLUSTER
```{r, eval = F}
# library(methylKit)
# 
# ls_files = as.list(c(list.files('./BAMs/AtF3', full.names=T), list.files('./BAMs/LMF3', full.names=T)))
# 
# print(ls_files)
# 
# myobj <- processBismarkAln(ls_files, sample.id = list("AtF3-1","AtF3-2","AtF3-3",
#                                                      "LMF-1", 'LMF-2', 'LMF-4'), read.context = 'CpG',
#                                                       treatment = c(1,1,1,0,0,0), assembly = 'atf3_vs_lmf3', mincov=1)
# 
# obj_tiled = tileMethylCounts(myobj, win.size = 1000, step.size = 500, mc.cores = 32, cov.bases = 0)
# 
# myobj.norm <- normalizeCoverage(obj_tiled, method = "median")
# 
# #meth_1l=unite(myobj.norm, destrand=FALSE, min.per.group=1L)
# meth_2l=unite(myobj.norm, destrand=FALSE, min.per.group=2L)
# meth_3l=unite(myobj.norm, destrand=FALSE, min.per.group=3L)
# 
# #cal_meth_1l <- calculateDiffMeth(meth_1l, adjust="fdr")
# cal_meth_2l <- calculateDiffMeth(meth_2l, adjust="fdr")
# cal_meth_3l <- calculateDiffMeth(meth_3l, adjust="fdr")
# 
# #de_meth_1l <- getMethylDiff(cal_meth_1l, qvalue = 0.01, difference=25)
# de_meth_2l <- getMethylDiff(cal_meth_2l, qvalue = 0.01, difference=25)
# de_meth_3l <- getMethylDiff(cal_meth_3l, qvalue = 0.01, difference=25)
# 
# print(de_meth_1l)
# print(de_meth_2l)
# print(de_meth_3l)
# 
# #write.csv(de_meth_1l, 'table_atf3_vs_lmf3_cpg_1l_1000_step_500.csv')
# write.csv(de_meth_2l, 'table_atf3_vs_lmf3_cpg_2l_1000_step_500.csv')
# write.csv(de_meth_3l, 'table_atf3_vs_lmf3_cpg_3l_1000_step_500.csv')
# save(meth_2l, meth_3l, myobj.norm, file= 'meth_kit_atf3_vs_lmf3_cpg.RData')
```


```{r, echo=F}
setwd('~/R/Fusarium_Flax/DE_Methyl/')
load('QC.RData')
# my_files <- list.files(path = ".", pattern = "*.RData", full.names = T)
# 
# temp <- new.env()
# lapply(my_files, load, temp)
# 
# all_data <- as.list(temp)
# rm(temp) 
# 
# bind_rows(all_data)
```


## MBias plots:

Charaterisctic of **reads**. Shows mean methylation percentage in every position

**Function for reading files**
```{r}
read_mbias <- function(sample_name, num, R){
  
chg = read.table(paste(sample_name,'/M', sample_name,'-',num,'_pe.CHG.(',R ,').M-bias.txt', sep = ''),
                 skip = 2, comment.char = '%', header = T)

chh = read.table(paste(sample_name, '/M', sample_name,'-',num, '_pe.CHH.(',R ,').M-bias.txt', sep = ''),
                 skip = 2, comment.char = '%', header = T)

cpg = read.table(paste(sample_name, '/M', sample_name,'-',num,'_pe.CpG.(',R ,').M-bias.txt', sep = ''),
                 skip = 2, comment.char = '%', header = T)
return(list(chg, chh, cpg, sample_name, R))
}
```

**Function for plotting**
```{r}
mbias_plot <-  function(list_data){
ggplot() + 
  geom_line(data = list_data[[1]], aes(x = position, y=count.1, col = 'red')) +
  geom_line(data = list_data[[2]], aes(x = position, y=count.1, col = 'blue')) +
  geom_line(data = list_data[[3]], aes(x = position, y=count.1, col = 'green')) +
  # geom_smooth(data = list_data[[1]], aes(x = position, y=count.1, col = 'red')) +
  # geom_smooth(data = list_data[[2]], aes(x = position, y=count.1, col = 'blue')) +
  # geom_smooth(data = list_data[[3]], aes(x = position, y=count.1, col = 'green')) +
  scale_color_manual(values = c('red', 'blue', 'green'), name="Position", 
                     labels=c('CHG','CHH','CpG')) +
  labs(title = paste(list_data[[4]], list_data[[5]], 'methylation percentage per postion'),
      x = 'sites', y = 'Methylation (%)')
}
```

```{r warning=FALSE, echo=F}
setwd('./mbias_lmf_atf_3/')

meth_atf1_r1 = read_mbias('AtF3', '1', 'R1')
meth_atf2_r1 = read_mbias('AtF3', '2', 'R1')
meth_atf3_r1 = read_mbias('AtF3', '3', 'R1')

meth_atf1_r2 = read_mbias('AtF3', '1', 'R2')
meth_atf2_r2 = read_mbias('AtF3', '2', 'R2')
meth_atf3_r2 = read_mbias('AtF3', '3', 'R2')

meth_lmf1_r1 = read_mbias('LMF3', '1', 'R1')
meth_lmf2_r1 = read_mbias('LMF3', '2', 'R1')
meth_lmf4_r1 = read_mbias('LMF3','4', 'R1')

meth_lmf1_r2 = read_mbias('LMF3','1', 'R2')
meth_lmf2_r2 = read_mbias('LMF3','2', 'R2')
meth_lmf4_r2 = read_mbias('LMF3','4', 'R2')
```

### Plots for each raeds library (ecah replicate, forward and reverse)
```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
mbias_plot(meth_atf1_r1)
mbias_plot(meth_atf1_r2)

mbias_plot(meth_atf2_r1)
mbias_plot(meth_atf2_r2)

mbias_plot(meth_atf3_r1)
mbias_plot(meth_atf3_r2)

mbias_plot(meth_lmf1_r1)
mbias_plot(meth_lmf1_r2)

mbias_plot(meth_lmf2_r1)
mbias_plot(meth_lmf2_r2)

mbias_plot(meth_lmf4_r1)
mbias_plot(meth_lmf4_r2)
```

## Percentage of methylation

### CpG sites
```{r echo=FALSE, fig.height=5.5, fig.width=7}
for (i in 1:6) {
  getMethylationStats(myobj_cpg.norm[[i]],plot=T,both.strands=FALSE, labels = T)
}
```

### CHH sites
```{r echo=FALSE, fig.height=5.5, fig.width=7}
for (i in 1:6) {
  getMethylationStats(myobj_chh.norm[[i]],plot=T,both.strands=FALSE, labels = T)
}
```


### CHG sites
```{r echo=FALSE, fig.height=5.5, fig.width=7}
for (i in 1:6) {
  getMethylationStats(myobj_chg.norm[[i]],plot=T,both.strands=FALSE, labels = T)
}
```

## Correlation

### CpG

#### _For uniting 3 replicates_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_3l_cpg ,plot=T, method = 'spearman')
```

#### _For uniting 2 replicates - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_2l_cpg ,plot=F, method = 'spearman')
```

#### _For uniting 1 replicate - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_1l_cpg ,plot=F, method = 'spearman')
```

### CHH

#### _For uniting 3 replicates_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_3l_chh ,plot=T, method = 'spearman')
```

#### _For uniting 2 replicates - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_2l_chh ,plot=F, method = 'spearman')
```

#### _For uniting 1 replicate - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_1l_chh ,plot=F, method = 'spearman')
```

### CHG

#### _For uniting 3 replicates_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_3l_chg ,plot=T, method = 'spearman')
```

#### _For uniting 2 replicates - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_2l_chg ,plot=F, method = 'spearman')
```

#### _For uniting 1 replicate - same plot_
```{r, echo=FALSE, warning=FALSE, fig.height=8, fig.width=10}
getCorrelation(meth_1l_chg ,plot=F, method = 'spearman')
```



## Looking through clusterization depending on correlation 

### CpG

#### _For uniting 3 replicates_
```{r echo=FALSE, message=FALSE}
clusterSamples(meth_3l_cpg, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 2 replicates - same_
```{r, echo=FALSE, eval=FALSE}
clusterSamples(meth_2l_cpg, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 1 replicates -same_
```{r eval=FALSE, echo=FALSE}
clusterSamples(meth_1l_cpg, dist="euclidean", method="ward", plot=TRUE)
```


### CHH

#### _For uniting 3 replicates_
```{r echo=FALSE, message=FALSE}
clusterSamples(meth_3l_chh, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 2 replicates - same_
```{r, echo=FALSE, eval=FALSE}
clusterSamples(meth_2l_chh, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 1 replicates -same_
```{r eval=FALSE, echo=FALSE}
clusterSamples(meth_1l_chh, dist="euclidean", method="ward", plot=TRUE)
```

### CHG

#### _For uniting 3 replicates_
```{r echo=FALSE, message=FALSE}
clusterSamples(meth_3l_chg, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 2 replicates - same_
```{r, echo=FALSE, eval=FALSE}
clusterSamples(meth_2l_chg, dist="euclidean", method="ward", plot=TRUE)
```

#### _For uniting 1 replicates -same_
```{r eval=FALSE, echo=FALSE}
clusterSamples(meth_1l_chg, dist="euclidean", method="ward", plot=TRUE)
```


## Let's see PCA

### CpG

#### Screeplot
```{r fig.height=4, fig.width=5}
PCASamples(meth_3l_cpg, screeplot=TRUE)
```


####  _For uniting 3 replicates_
```{r echo=FALSE, fig.height=5, fig.width=5}
PCASamples(meth_3l_cpg)
```

#### _For uniting 2 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5, eval=FALSE}
PCASamples(meth_2l_cpg)
```

#### _For uniting 1 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5,eval=FALSE}
PCASamples(meth_1l_cpg)
```

### CHH

#### Screeplot
```{r fig.height=4, fig.width=5}
PCASamples(meth_3l_chh, screeplot=TRUE)
```


####  _For uniting 3 replicates_
```{r echo=FALSE, fig.height=5, fig.width=5}
PCASamples(meth_3l_chh)
```

#### _For uniting 2 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5, eval=FALSE}
PCASamples(meth_2l_chh)
```

#### _For uniting 1 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5,eval=FALSE}
PCASamples(meth_1l_chh)
```

### CHG

#### Screeplot
```{r fig.height=4, fig.width=5}
PCASamples(meth_3l_chg, screeplot=TRUE)
```


####  _For uniting 3 replicates_
```{r echo=FALSE, fig.height=5, fig.width=5}
PCASamples(meth_3l_chg)
```

#### _For uniting 2 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5, eval=FALSE}
PCASamples(meth_2l_chg)
```

#### _For uniting 1 replicates - same_
```{r echo=FALSE, fig.height=4, fig.width=5,eval=FALSE}
PCASamples(meth_1l_chg)
```
